MIP-GNN: A data-driven tool for guiding combinatorial solvers

### 2021-03-10 paper/main.tex
Cont. implementing new model.
e
MC.

%\begin{algorithm}[H]\mbox{\hfill}
%	\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
%	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
%	\begin{algorithmic}[1]
%		\State Initialize constraint weights $\vec{w}_i \leftarrow 1$ for $i$ in $[m]$ 
%		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for $i$ in $[m]$ 
%		\State Set $T$ to according~\cref{mwubound}
%		\For{$t \text{ in } [T]$}
%		
%		\State Call oracle: $\vec{x} \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$, \textbf{if} $
%		\vec{x} = \emptyset$ \Return  \texttt{non-feasible}
%		\State Compute error signal $\vec{e}$, where
%		\begin{equation*}
%		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_j\trans \vec{x}(t) - \vec{b}_j)   
%		\end{equation*}
%		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
%		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
%		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
%		\EndFor
%		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T} $
%	\end{algorithmic}
%	\caption{MWU for the LP feasibility problem.}
%	\label{alg:as}
%\end{algorithm}
\cm{exploration/exploitation $\eta$}
Same algorithm as above interpreted as a message passing algorithm:
\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:} Biparite constraint graph $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
	\begin{algorithmic}[1]
		\State Initialize weights $\vec{w}_j \leftarrow 1$ for each constraint node
		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for each constraint node
		\State Set $T$ to according~\cref{mwubound}
		\For{$t \text{ in } [T]$}
		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable
		\Statex
		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$
		\begin{equation*}
		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
		\end{equation*}
		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
		\EndFor
		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T}$
	\end{algorithmic}
	\caption{MWU (Message passing version) for the LP feasibility problem.}
	\label{alg:as}
\end{algorithm}

@@

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:}  Training set $S$, number of epochs $E$, number of layers $T$.  \\
	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$.
	\begin{algorithmic}[1]
		\State Initialize $\vec{v}^{(0)}$, $\vec{c}^{(0)}$, and $\vec{p}_i^{(0)}$
		\Statex
		\For{$e \text{ in } [E]$}
		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ from $U(S)$ 
		\For{$t \text{ in } [T]$}
		%\State \textit{Compute variable embedding:}
		\State $\vec{V}_j^{(t)} \leftarrow f_{\textsc{Var}}^{(t)} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{V}^{(t-1)}_j, \vec{C}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ij} \big)\hspace{-1pt} \mid c_i \in N(v_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $j$ in $[n]$ 		
		\State $\vec{X}_j^{(t)} \leftarrow f_\textsc{Assn}^{(t)} \hspace{-2pt} \big(\vec{V}_i^{(t-1)} \big)$ for all $j$ in $[n]$ 
		\Statex
		%\State \textit{Compute constraint embedding:}
		\State $\vec{C}_j^{\hspace{1pt}(t)} \leftarrow f_\textsc{Con}^{(t)} \hspace{-2pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{C}^{(t-1)}_j, \vec{V}^{(t)}_i, \vec{X}^{(t)}_i, \vec{A}_{ij}, \vec{b}_j \big)\hspace{-2pt} \mid v_i \in N(c_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[m]$ 	
		%\State $\vec{e}_j^{(t)} \leftarrow \sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{x}_i - \vec{b}_j$
		%\Statex
		\State $\vec{p}_{j}^{(t)} \hspace{3pt}\leftarrow \text{softmax}(f_\textsc{Prob}^{(t)}(\vec{e}^{(t)}))_{j}$
		%\begin{equation*}
		%\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  %\vec{v}_i \Big) - \vec{b}_j   
		%\end{equation*}
		\EndFor
		\State $\bar{\vec{X}}_j \leftarrow f_\textsc{Mrg}(\mathbin\Vert_{t \in [T]} \vec{X}_j^{(t)})$
		\State $L \leftarrow L + \ell(\vec{\bar{X}}, \vec{\bar b})$ 
		\State Gradient descent  with regard to $\boldsymbol{\theta}$
		\EndFor
		\State \Return $\boldsymbol{\theta}$

@@

\begin{equation}\label{err}
\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
\end{equation}

@@

\cm{Somehow show that architecture of Alg. 2 (MWU) is better than using a standard GNN. Idea: Show that MWU can be recovered to show to always get at ferasible solutions.}

@@

Our intention here is to investigate the benefits of ... the compared to...
More precisely, we address the following questions:\\
\begin{description}
	\item[Q1] description
	\item[Q2] description
	\item[Q3] description
\end{description}

>>>>

%\begin{algorithm}[H]\mbox{\hfill}
%	\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
%	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
%	\begin{algorithmic}[1]
%		\State Initialize constraint weights $\vec{w}_i \leftarrow 1$ for $i$ in $[m]$ 
%		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for $i$ in $[m]$ 
%		\State Set $T$ to according~\cref{mwubound}
%		\For{$t \text{ in } [T]$}
%		
%		\State Call oracle: $\vec{x} \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$, \textbf{if} $
%		\vec{x} = \emptyset$ \Return  \texttt{non-feasible}
%		\State Compute error signal $\vec{e}$, where
%		\begin{equation*}
%		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_j\trans \vec{x}(t) - \vec{b}_j)   
%		\end{equation*}
%		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
%		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
%		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
%		\EndFor
%		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T} $
%	\end{algorithmic}
%	\caption{MWU for the LP feasibility problem.}
%	\label{alg:as}
%\end{algorithm}
\cm{exploration/exploitation $\eta$}
Same algorithm as above interpreted as a message passing algorithm:
\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:} Biparite constraint graph $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
	\begin{algorithmic}[1]
		\State Initialize weights $\vec{w}_j \leftarrow 1$ for each constraint node
		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for each constraint node
		\State Set $T$ to according~\cref{mwubound}
		\For{$t \text{ in } [T]$}
		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
		\State Send $\vec{v}_i$ to each adjacent constraint
		\State Compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$
		\begin{equation*}
		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
		\end{equation*}
		\State Update $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
		\EndFor
		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T}$
	\end{algorithmic}
	\caption{MWU (Message passing version) for the LP feasibility problem.}
	\label{alg:as}
\end{algorithm}

@@

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:}  Training set $S$, number of epochs $E$, number of layers $T$.  \\
	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$.
	\begin{algorithmic}[1]
		\State Initialize $\vec{v}^{(0)}$, $\vec{c}^{(0)}$, and $\vec{p}_i^{(0)}$
		\Statex
		\For{$e \text{ in } [E]$}
		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ from $U(S)$ 
		\For{$t \text{ in } [T]$}
		\State $\vec{V}_j^{(t)} \leftarrow f_{\textsc{Var}}^{(t)} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{V}^{(t-1)}_j, \vec{C}^{(t-1)}_j, \vec{p}^{(t-1)}_i, \vec{A}_{ij} \big)\hspace{-1pt} \mid c_i \in N(v_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $j$ in $[n]$ 		
		\State $\vec{X}_j^{(t)} \leftarrow f_\textsc{Assn}^{(t)} \hspace{-2pt} \big(\vec{V}_j^{(t-1)} \big)$ 
		\Statex
		%\State \textit{Compute constraint embedding:}
		\State $\vec{C}_i^{\hspace{1pt}(t)} \leftarrow f_\textsc{Con}^{(t)} \hspace{-2pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{C}^{(t-1)}_i, \vec{V}^{(t)}_i, \vec{X}^{(t)}_i, \vec{A}_{ij}, \vec{b}_i \big)\hspace{-2pt} \mid v_i \in N(c_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[m]$ 	
		%\State $\vec{e}_j^{(t)} \leftarrow \sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{x}_i - \vec{b}_j$
		%\Statex

		\State $\vec{p}_{i}^{(t)} \hspace{3pt}\leftarrow \text{softmax}(f_\textsc{Prob}^{(t)}(\vec{e}^{(t)}))_{i}$
		%\begin{equation*}
		%\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  %\vec{v}_i \Big) - \vec{b}_j   
		%\end{equation*}
		\EndFor
		\State $\bar{\vec{X}}_j \leftarrow f_\textsc{Mrg}(\mathbin\Vert_{t \in [T]} \vec{X}_j^{(t)})$
		\State $L \leftarrow L + \ell(\vec{\bar{X}}, \vec{\bar b})$ 
		\State Gradient descent  with regard to $\boldsymbol{\theta}$
		\EndFor
		\State \Return $\boldsymbol{\theta}$

@@

\begin{equation}\label{err}
\vec{e}_i \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{j \in N(i)} \vec{A}_{ij}  \vec{X}_j \Big) - \vec{b}_i   
\end{equation}

@@

\cm{Somehow show that architecture of Alg. 2 (MWU) is better than using a standard GNN. Idea: Show that MWU can be recovered to show that we always get an (epsilon) feasible solution (on the test data)}

@@

Our intention here is to investigate the benefits of ... the compared to...
More precisely, we address the following questions:\\

\cm{}
\begin{description}
	\item[Q1] description
	\item[Q2] description
	\item[Q3] description
\end{description}
